---
title: "Nd-in-brief-Figures"
author: "Esther Plomp & Joshua Peterson"
date: "31-7-2021"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Credit
These scripts were built upon code made available by Chris Stantis: 
Chris Stantis. (2021). stantis/IsoDataVis: First (Official) Release (v1.2). Zenodo.https://doi.org/10.5281/zenodo.4743735

You are free to reuse these scripts using a CC-BY/MIT license.

Plomp E., Peterson J.C. (2021). Figures-Nd-data (version 1.0.0).https://github.com/EstherPlomp/Figures-Nd-data (check the CITATION.CFF file in the repository for the DOI)


## Dependencies

```{r, warning=FALSE}
library("tidyverse")
```

## Import data Figure 1
Copy the .csv dataset from the GitHub repro (https://github.com/EstherPlomp/Figures-Nd-data/blob/main/Data/Nd-data-Figure1.csv)

```{r data Figure 1}
Figure1 = read.csv("Nd-data-Figure1.csv", sep = ";" , row.names = NULL)
Figure1$X143Nd.144Nd = as.numeric(gsub(",", ".", gsub("\\.", "", Figure1$X143Nd.144Nd))) #Remove commas so that it can be read as a number
Figure1$SD = as.numeric(gsub(",", ".", gsub("\\.", "", Figure1$SD))) #Remove commas so that it can be read as a number
Figure1$SDmin <- Figure1$X143Nd.144Nd - Figure1$SD #Add the minimum value for the error bars based on SD
Figure1$SDmax <- Figure1$X143Nd.144Nd + Figure1$SD #Add the max value for the error bars based on SD
```

## Figure 1

```{r}
ggplot(Figure1) +
  geom_errorbar(aes(x= Sample_Reference, ymin = SDmin, ymax = SDmax, width = 0.2)) +
  geom_point(aes(x= Sample_Reference, y=X143Nd.144Nd, shape=Country, color=Country), size = 4) + 
    theme_classic() +
  scale_x_continuous(breaks=seq(0,40,5)) +
  scale_shape_manual(values=c(15, 16, 17, 18, 19, 17)) +
  scale_color_manual(values = c("#f9d90f", "#c81025", "#002a7b", "#00765b", "#9e12a7", "#e98a2e")) +
  theme(
    legend.position = c(0.1, 0.8), 
    legend.background = element_rect(size = 0.5, linetype="solid", colour ="grey"))+ 
  ggtitle("Neodymium ratios") +
  theme(plot.title = element_text(size=22, hjust = 0.5))+
  labs(
    x = "Individuals sorted on Sample Reference (Table 1)",
    y = expression(paste(""^143, "Nd/", ""^144, "Nd" )),
  ) 
```


## Import data Figure 2

```{r}
Figure2 = read.csv("Nd-data-Figure2.csv", sep = ";" , row.names = NULL)
Figure2$X143Nd.144Nd = as.numeric(gsub(",", ".", gsub("\\.", "", Figure2$X143Nd.144Nd))) 
Figure2$X87Sr.86Sr = as.numeric(gsub(",", ".", gsub("\\.", "", Figure2$X87Sr.86Sr))) 
```

## Figure 2
Copy the .csv dataset from the GitHub repro (https://github.com/EstherPlomp/Figures-Nd-data/blob/main/Data/Nd-data-Figure2.csv)

```{r}
ggplot(Figure2) +
  geom_point(aes(x=X87Sr.86Sr, y=X143Nd.144Nd, shape=Country, color=Country), size = 4) + 
  theme_classic() +
  xlim(0.7078,0.7119)+
  scale_shape_manual(values=c(15, 16, 17, 18, 19, 17)) +
  scale_color_manual(values = c("#f9d90f", "#c81025", "#002a7b", "#00765b", "#9e12a7", "#e98a2e")) +
  theme(
    legend.position = c(0.8, 0.7), 
    legend.background = element_rect(size = 0.5, linetype="solid", colour ="grey")
  ) +
  ggtitle("Neodymium and strontium ratios") +
  theme(plot.title = element_text(size=22, hjust = 0.5))+ #center title
  labs(
    x = expression(paste(""^87, "Sr/", ""^86, "Sr" )),
    y = expression(paste(""^143, "Nd/", ""^144, "Nd" ))
  ) 

```


